Neural and Symbolic Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation

### 2023-02-07 docs/papers/sto/sto.tex
FIXUP draft: change title, add TODO

\title[Spatiotemporally Optimized Simulation]
{Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation}

@@

>>>>

\title[Spatiotemporally Optimized Simulation]
{Neural and Symbolic Spatiotemporal Optimization of Cosmological
Particel-Mesh Simulation}

@@

\section*{TODO}
\begin{itemize}
\item Non-integer multiple mesh shapes: for uniform particle grid, test
  (with double precision on CPUs) whether they start moving by artifact
  forces on cell scales, in 3 cases: no deconvolution, with CIC
  deconvolution, with SO.
\item For TO, probably necessary to first incorporate Oliver Hahn's
  recent improvement on FastPM integrator arXiv:2301:09655.
\end{itemize}
